\documentclass[11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{enumitem}
\usepackage{textcomp}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}


% -----------------------------------------------------------
% Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


% -----------------------------------------------------------
% Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}
% -----------------------------------------------------------
% Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-4pt}}
\newcommand{\resheading}[1]{
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
      \setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-11pt}
}
\newcommand{\ressubheading}[4]{
  \begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\

  \end{tabular*}\vspace{-6pt}}

\newcommand{\school}[4]{\vspace{1.5mm}
  \textbf{#1} \hfill #2 \textit{#3} \hfill \textit{#4} \vspace{1.5mm}
}

\newcommand{\job}[4]{
  \textbf{#1} \hfill #2 \hfill \textit{#3} \hfill \textit{#4}
}

\newcommand{\skill}[2]{\vspace{1.5mm}
  \textbf{#1} #2
}

\newcommand{\certificate}[3]{
  \textbf{#1} #2 \hfill \textit{#3} 
}

\newcommand{\project}[4]{ \vspace{1.5mm}
  \textbf{#1} #2 \hfill \textit{#3}#4 \vspace{1.5mm}
}

\newcommand{\award}[4]{ \vspace{1.5mm}
  \textbf{#1} #2 \hfill \textit{#3} #4 \vspace{1.5mm}
}
% -----------------------------------------------------------
\begin{document}
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Sanad Kadu} & \textit{sanaddilipkadu@gmail.com | +91-9604484805 | India | https://github.com/cypherBeep}
\end{tabular*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\resheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{itemize}[leftmargin=*]
  
\item[]
  \school
  {UPES}
  {Dehradun, Uttarakhand\\}
  {B.Tech CSE - Spl. CC\&VT, GPA: 7.89}
  {Aug 2018 - Apr 2022}
\item[]
  \school
  {Vinyak Vidya Mandir}
  {Amravati, Maharashtra\\}
  {State Board XII Std, Percentage: 85.85\%}
  {}
\item[]
  \school
  {School Of Scholars}
  {Amravati, Maharashtra\\}
  {CBSE Class 10th, Percentage: 86.2\%}
  {}
  
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\resheading{Projects}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{itemize}[leftmargin=*]
\item[]
  \project
  {Plagarism Detector}
  {C, GCC, CMake}
  {https://github.com/cypherBeep/Plagiarism-Detection}
  {\\A C excecutable which can detect percent of plagarism between two text files using different plagarism detection algorithms that use k-grams viz. KMP, Winnowing, Rabin-Karp and Naive String Matching.}
\item[]
  \project
  {Debord Bot}
  {Javascript, Heroku, Node JS}
  {https://github.com/cypherBeep/debord-bot}
  {\\A bot which uses puppeteer package to fetch quotes of Guy Debord from internet and strore them in spreadsheets on cloud then tweet those using Twitter API at regular intervals.}
\item[]
  \project
  {Virtual Machine Translator}
  {Javascript, Assembly, HDL}
  {https://github.com/cypherBeep/nand2tetris}
  {\\An stack based implementation of the classic VM Translator which can translate Hack language assembly code to VM code for a 16-bit machine architecture made from scratch.}
\item[]
  \project
  {Hayek Token}
  {Solidity, Truffle, Javascript}
  {https://github.com/cypherBeep/Hayek-Token}
  {\\Implementation of crypto token as per ERC20 standard built on Ethereum to use as an asset in the hospitality industry and loyalty programs.}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\resheading{Skills and Interests}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{itemize}[leftmargin=*]
  \setlength\itemsep{0em}
\item[] \skill{* Programming Languages:}{Javascript (preferred), C, Java, Rust, Bash, Solidity, Lisp.}
\item[] \skill{* Technologies and Tools/Frameworks:}{Node JS, JQuery, PostgreSQL, Emacs, Linux, Distributed Systems, Git, Truffle.}
\item[] \skill{* Technical Skills:}{Software Engineering, System Administration, Backend Managment.}
\item[] \skill{* Interests:}{Decentralization Technologies, Blockchains, Ethereum Development, Cloud Computing.}
\item[] \skill{*}{Discovering and implementing new ideas. Give me an API and a problem and I\textquotesingle{}ll figure it out.}
\item[] \skill{*}{I can readily learn and adapt to a new discpline, area or environmet and start pushing real results quickly.}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\resheading{Certificates}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{itemize}[leftmargin=*]
\item[]
  \certificate
  {Build a Modern Computer from First Principles: From Nand to Tetris\\}
  {Issuing Organization: Coursera}
  {https://www.coursera.org/account/accomplishments/certificate/ZLWJJD4NS6A3}
\item[]
  \certificate
  {Software Development Processes and Methodologies\\}
  {Issuing Organization: Coursera}
  {https://www.coursera.org/account/accomplishments/certificate/QG39TCSVBRTZ}
\item[]
  \certificate
  {Introduction to Software Product Management\\}
  {Issuing Organization: Coursera}
  {https://www.coursera.org/account/accomplishments/certificate/PH8C62QQPWP9}
\item[]
  \certificate
  {Introduction to Git and GitHub\\}
  {Issuing Organization: Coursera}
  {https://www.coursera.org/account/accomplishments/certificate/EBSSXZXK428D}
\item[]
  \certificate
  {The Arts and Science of Relationships: Understanding Human Needs\\}
  {Issuing Organization: Coursera}
  {https://www.coursera.org/account/accomplishments/certificate/ERP6V6WKVKUB}
\item[]
  \certificate
  {Introduction to Psychology\\}
  {Issuing Organization: Coursera}
  {https://www.coursera.org/account/accomplishments/certificate/WJ3RR4WXTSKM}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\resheading{Achievements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{itemize}[leftmargin=*]
\item[]
  \award
  {Project Expo Winner}
  {Dec 2020}
  {UPES}
  {\\Won the best project award for Plagarism Detector in annual university competition.}
\end{itemize}
\ 
\end{document}